WunderPass-White-Paper

### 2022-01-31 [05][Economics]/[Economics][Quantifizierung].tex
REFACTORING

% !TEX root = paper.tex
\subsection{Quantifizierung}
\label{sec:eco_zahlen}
\todo{Einleitung - Start}

@@

\input{[Economics][Quantifizierung][Definitionen]}    % binde die Datei '[Economics][Quantifizierung][Definitionen].tex' ein

@@

\input{[Economics][Quantifizierung][WP][Status quo]} % binde die Datei '[Economics][Quantifizierung][WP][Status quo].tex' ein

\input{[Economics][Quantifizierung][WP][Messbarkeit]} % binde die Datei '[Economics][Quantifizierung][WP][Messbarkeit].tex' ein

\input{[Economics][Quantifizierung][WP][Fazit]} % binde die Datei '[Economics][Quantifizierung][WP][Fazit].tex' ein

@@

\input{[Economics][Quantifizierung][deprecated]}    % binde die Datei '[Economics][Quantifizierung][deprecated].tex' ein

>>>>

% !TEX root = C:/Users/Slava/White-Paper/[05][Economics]/Economics.tex

\subsection{Quantifizierung}
\label{sec:eco_zahlen}
\todo{Einleitung - Start}

@@

\input{C:/Users/Slava/White-Paper/[05][Economics]/[Economics][Quantifizierung][Definitionen]}    % binde die Datei '[Economics][Quantifizierung][Definitionen].tex' ein

@@

\input{C:/Users/Slava/White-Paper/[05][Economics]/[Economics][Quantifizierung][WP][Status quo]} % binde die Datei '[Economics][Quantifizierung][WP][Status quo].tex' ein

\input{C:/Users/Slava/White-Paper/[05][Economics]/[Economics][Quantifizierung][WP][Messbarkeit]} % binde die Datei '[Economics][Quantifizierung][WP][Messbarkeit].tex' ein

\input{C:/Users/Slava/White-Paper/[05][Economics]/[Economics][Quantifizierung][WP][Fazit]} % binde die Datei '[Economics][Quantifizierung][WP][Fazit].tex' ein

@@

\input{C:/Users/Slava/White-Paper/[05][Economics]/[Economics][Quantifizierung][deprecated]}    % binde die Datei '[Economics][Quantifizierung][deprecated].tex' ein

### 2022-01-31 [05][Economics]/[Economics][Quantifizierung][WP][Status quo].tex
REFACTORING

% !TEX root = paper.tex

@@

\input{[Economics][Quantifizierung][theoremPools]}    % binde die Datei '[Economics][Quantifizierung][theoremPools].tex' ein

>>>>

% !TEX root = [Economics][Quantifizierung].tex

@@

\input{C:/Users/Slava/White-Paper/[05][Economics]/[Economics][Quantifizierung][WP][Status quo][theoremPools]}    % binde die Datei '[Economics][Quantifizierung][WP][Status quo][theoremPools].tex' ein
